\chapter*{Abstract}

Data-driven models have emerged as a promising area of research in the field of \glspl{asv}.
These models have the potential to interpret sensor data and enhance situational awareness.
However, their effectiveness heavily relies on large quantities of high-quality data for training, testing, and validation purposes.

In this \master, I have completed the development of a human-operable \sr for collecting high-quality data in maritime environments.
The \sr is IP67 rated and has two polarization cameras, an \gls{imu}, and two \gls{gnss} receivers, all synchronized to UTC time.
The \sr also exposes two additional $1Gb/s$ Ethernet ports with PoE  enabling the connection of additional sensors.

A major technical achievement in this \master has been to levrage CUDA and GStreamer for on-the-fly hardware-accelerated video compression on the Jetson Xavier, significantly extending the recording time.
In adition, ergonomic hardware enhancements have been incorporated, along with the introduction of a new web-based user interface, streamlining the data acquisition process.
Finally a couple of small data sets were captured in field to demonstrate the capabilities of the sensor rig as a data collection platform.

This new low-threshold approach to acquiring high-quality data serves as a strong foundation for my future Ph.D. work and has garnered attention from external entities. Orders have been placed for the necessary components to create a second \sr, and discussions with external parties for funding a third \sr are currently underway. These developments clearly demonstrate the positive reception of the \sr and the recognized demand for such a system.

